\section{Oracle Coherence - DataGrid}
\index{Coherence}

Oracle Coherence In-Memory Data Grid is a data management platform
``for application objects that are shared across multiple servers,
require low response time, very high throughput, predictable
scalability, continuous availability and information
reliability''\cite~{hid-sp18-514-OracleCoherence}. Initially this
framework was built by Tangosol Inc. ``The Tangosol Inc., was acquired
by Oracle Corporation in 2007''~\cite{hid-sp18-514-coherencewiki} and
named that framework as Oracle Coherence.Oracle coherence is best
suitable for computational intensive, stateful middle-ware
applications that runs in a distributed platform. Coherence is
directed to run application layer, and is often run in-memory with
application itself. ``Data Grid is a system of composed of multiple
servers that work to manage information and related operations.
Coherence provides the ideal infrastructure for building Data Grid
services, and the client and server-based applications that use a Data
Grid. At a basic level, Coherence can manage an immense amount of data
across a large number of servers in a grid; it can provide close to
zero latency access for that data; it supports parallel queries across
that data; and it supports integration with database and EIS systems
that act as the system of record for that data. Additionally,
Coherence provides several services that are ideal for building
effective data grids''~\cite{hid-sp18-514-OracleCoherence}. This
framework comes by default with Oracle WebLogic 12c server. Oracle
also provides standalone coherence server, which can be used in any
Big Data environment to store any database data, inflight or any
dataset to be processed by MapReduce or any other Hadoop component.
Cache servers (JVM’s) can be configured in the clusters. This framework
can be used in the Big Data environment without HDFS for in-memory
distributed data storage. There are DOT NET, JAVA, C++ and other API’s
available along with REST service to access Coherence
cache\cite{hid-sp18-514-OracleCoherence}. Oracle coherence can be
integrated from Spring based distributed applications as
well\cite{hid-sp18-514-CoherenceSpringInt}.
