\section{Tibco DataSynapse GridServer}
\index{DSGridServer}

“DataSynapse was founded by two ex-investment bankers with an idea to speed up calculations by running them in parallel, 
distributed over multiple machines. The first product live cluster was released in 2001. 
In 2004 this product was renamed to GridServer. Gridserver was developed to support larger 
and larger grid of network computers”~\cite{hid-sp18-514-datasynapsewiki}.
DataSyanpse was acquired by Tibco in 2009 and later this product was renamed as: 
Tibco DataSynapse GridServer\cite{hid-sp18-514-tibcodatasynapsewiki}.
“GridServer is a highly scalable software infrastructure that allows application services to operate in a virtualized fashion, 
unattached to specific hardware resources. Client applications submit requests to the Grid environment 
and GridServer dynamically provisions services to respond to the request. 
Multiple client applications can submit multiple requests in parallel and GridServer dynamically 
creates multiple service instances to handle requests in parallel on different Grid nodes. 
This architecture is therefore highly scalable in both speed and throughput. For example, 
a single client will see scalable performance gains in the processing of multiple requests, 
and many applications and users will see scalable throughput of the aggregate load”~\cite{hid-sp18-514-tibcods}.
Data Synapse grid server has the capabilities of compute grid and data grid. The main components of the grid server are Engines, 
Directors and Brokers. All these components are JVM’s built in Java.  
Each component has their own responsibilities. The applications are deployed in the engines and computation and processing 
is also done in the engines. Engines are light weight containers. Directors receive the client requests 
and then navigate to the broker. Broker act as a load balancer to navigate the request to the available engines 
in the grid environment based on engine load, availability and etc.\ As there are multiple nodes in the grid, 
there will be primary and secondary director, broker, and several engines to support high availability 
and fault tolerance\cite{hid-sp18-514-tibcods}.For more details on this product 
please go through the PDF documents at below link

% NO URLS ARE ALLOWED IN ABSTRACTS ALSO YOU ARE NOT FOLLOWING chktex https://docs.tibco.com/products/tibco-datasynapse-gridserver-6-2-0.
